PR 2 Pengantar Sains Komputasi

### 2022-10-05 Semester III/Pengantar SK/PR 2/PR 20921004.Rmd
new

---
title: "PR 2 Pengantar Sains Komputasi"
subtitle: "20921004 Mohammad Rizka Fadhli"
output: pdf_document
date: '5 Oktober 2022'
---

>>>>

---
title: "PR 2 Pengantar Sains Komputasi"
subtitle: "20921004 Mohammad Rizka Fadhli"
output: pdf_document
linestretch: 1.5
fontsize: 12pt
date: '5 Oktober 2022'
---
